Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
some changes

\ab{For the EFT of GR with dimension-eight operators, Ref.~\cite{Sennett:2019bpc} focused on the 
orbital effects (i.e., the inspiral stage) and performed 
Bayesian model selection using the two lowest-mass BBHs events of the second-observig run of 
the LIGO-Virgo Collaboration, notably GW151226 and GW170608. They found that the 
data disfavor the appearance of new physics on distance scales around $\ell_{\rm qEFT} \sim 150$ km.}

>>>>

\ab{For the EFT of GR with dimension-eight operators, Ref.~\cite{Sennett:2019bpc} focused on the 
orbital effects (i.e., instead of finite-size effects) and performed 
Bayesian model selection using the two lowest-mass BBHs events of the second-observig run of 
the LIGO-Virgo Collaboration, notably GW151226 and GW170608. They found that the 
data disfavor the appearance of new physics on distance scales around $\ell_{\rm qEFT} \sim 150$ km.}
